Comparing the Efficiency of Machine Learning and Deep Learning Models in Source Code Authorship Attribution

### 2025-03-02 article.tex
figure in progress... but almost done

\begin{figure}[h!]
\centering
\begin{tikzpicture}
\begin{axis}[
    view={60}{30},             % 3D viewing angles (azimuth, elevation)
    z buffer=sort,             % Ensures correct front-to-back rendering
    xlabel={Model},
    xlabel style={
        xshift = -40pt,
        yshift=40pt,
        align=center        % optional alignment
    },
    ylabel={Author set size},
    ylabel style={
        xshift = 25pt,
        yshift=20pt,
        align=center        % optional alignment
    },
    zlabel={Metric (\%)},
    width=14cm,
    height=8cm,
    xtick={1,2,3,4},
    xticklabels={RF (TF-IDF), BERT (source code), BERT (AST pre\_order), AttentionNN},
    xticklabel style={
        font=\footnotesize,   % or \footnotesize, \tiny, etc.
        xshift = -20pt,
        yshift=10pt,
        align=center        % optional alignment
    },
    ytick={1,2,3,4},
    yticklabels={3 (min. count 58), 11 (min. count 50), 27 (min. count 40), 110 (min. count 25)},
    yticklabel style={
        font=\footnotesize,   % or \footnotesize, \tiny, etc.
        xshift = 25pt,
        yshift=5pt,
        align=center        % optional alignment
    },
    zmin=0, zmax=100,
    grid=major,
    legend style={
        at={(0.5,1.15)},
        anchor=north,
        legend columns=3
    }
]

@@

\addplot3+[ybar, bar width=12pt, fill=blue, draw=none, bar shift=-0.2] 
    coordinates {(1.1,1,85.84) (1,2,80.56) (1,3,70.60) (1,4,66.24)};
\addplot3+[ybar, bar width=12pt, fill=red, draw=none, bar shift=0]  
    coordinates {(1.1,1,89.36) (1,2,84.56) (1,3,79.27) (1,4,71.73)};
\addplot3+[ybar, bar width=12pt, fill=brown, draw=none, bar shift=+0.2] 
    coordinates {(1.1,1,84.96) (1,2,72.03) (1,3,69.73) (1,4,65.55)};

\addplot3+[
    mark=none,
    blue,
    dotted,
    line width=1pt,
    nodes near coords,
    every node near coord/.append style={
        mark=none,
        fill=none,
        draw=none,
        text=black,
        font=\scriptsize,
        yshift=0pt
    }
] coordinates {
    (0.8,1,85.84) (0.8,2,80.56) (0.8,3,70.60) (0.8,4,66.24)
};

@@

\addplot3+[ybar, bar width=12pt, fill=blue, draw=none, bar shift=-0.2] 
    coordinates {(2,1,90.70) (2,2,89.84) (2,3,82.72) (2,4,72.47)};
\addplot3+[ybar, bar width=12pt, fill=red, draw=none, bar shift=0]  
    coordinates {(2,1,93.33) (2,2,90.33) (2,3,84.66) (2,4,76.69)};
\addplot3+[ybar, bar width=12pt, fill=brown, draw=none, bar shift=+0.2] 
    coordinates {(2,1,91.67) (2,2,89.92) (2,3,82.25) (2,4,71.76)};

\addplot3+[
    mark=none,
    blue,
    dotted,
    line width=1pt,
    nodes near coords,
    every node near coord/.append style={
        mark=none,
        fill=none,
        draw=none,
        text=black,
        font=\scriptsize,
        yshift=0pt
    }
] coordinates {
    (1.8,1,90.70) (1.8,2,89.84) (1.8,3,82.72) (1.8,4,72.47)
};

@@

\addplot3+[ybar, bar width=12pt, fill=blue, draw=none, bar shift=-0.2] 
    coordinates {(3,1,83.72) (3,2,40.62) (3,3,35.66) (3,4,24.07)};
\addplot3+[ybar, bar width=12pt, fill=red, draw=none, bar shift=0]  
    coordinates {(3,1,84.72) (3,2,40.53) (3,3,36.41) (3,4,27.40)};
\addplot3+[ybar, bar width=12pt, fill=brown, draw=none, bar shift=+0.2] 
    coordinates {(3,1,82.58) (3,2,38.30) (3,3,33.93) (3,4,23.33)};

\addplot3+[
    mark=none,
    blue,
    dotted,
    line width=1pt,
    nodes near coords,
    every node near coord/.append style={
        mark=none,
        fill=none,
        draw=none,
        text=black,
        font=\scriptsize,
        yshift=0pt
    }
] coordinates {
    (2.8,1,83.72) (2.8,2,40.62) (2.8,3,35.66) (2.8,4,24.07)
};

>>>>

\begin{figure}[h!]
\centering
\begin{tikzpicture}
\begin{axis}[
    view={60}{30},            % 3D viewing angles (azimuth, elevation)
    z buffer=sort,            % Ensures correct front-to-back rendering
    xlabel={Model},
    xlabel style={
        xshift = -40pt,
        yshift=40pt,
        align=center          % optional alignment
    },
    ylabel={Author set size},
    ylabel style={
        xshift = 25pt,
        yshift=20pt,
        align=center          % optional alignment
    },
    zlabel={Metric (\%)},
    width=14cm,
    height=8cm,
    xtick={1,2,3,4},
    xticklabels={RF (TF-IDF), BERT (source code), BERT (AST pre\_order), AttentionNN},
    xticklabel style={
        font=\footnotesize,    % or \footnotesize, \tiny, etc.
        xshift = -20pt,
        yshift=10pt,
        align=center          % optional alignment
    },
    ytick={4,3,2,1}, % Reversed ytick values
    yticklabels={3 (min. count 58), 11 (min. count 50), 27 (min. count 40), 110 (min. count 25)}, % Corresponding reversed labels
    yticklabel style={
        font=\footnotesize,    % or \footnotesize, \tiny, etc.
        xshift = 25pt,
        yshift=5pt,
        align=center          % optional alignment
    },
    zmin=0, zmax=100,
    grid=major,
    legend style={
        at={(0.5,1.15)},
        anchor=north,
        legend columns=3
    }
]

@@

\addplot3+[ybar, bar width=12pt, fill=blue, draw=none, bar shift=-0.2]
    coordinates {(1.1,4,85.84) (1,3,80.56) (1,2,70.60) (1,1,66.24)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=red, draw=none, bar shift=0]
    coordinates {(1.1,4,89.36) (1,3,84.56) (1,2,79.27) (1,1,71.73)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=brown, draw=none, bar shift=+0.2]
    coordinates {(1.1,4,84.96) (1,3,72.03) (1,2,69.73) (1,1,65.55)}; % Coordinates are adjusted to match the reversed ytick

\addplot3+[
    mark=none,
    blue,
    dotted,
    line width=1pt,
    nodes near coords,
    every node near coord/.append style={
        mark=none,
        fill=none,
        draw=none,
        text=black,
        font=\scriptsize,
        yshift=0pt
    }
] coordinates {
    (0.8,4,85.84) (0.8,3,80.56) (0.8,2,70.60) (0.8,1,66.24) % Coordinates are adjusted to match the reversed ytick
};

@@

\addplot3+[ybar, bar width=12pt, fill=blue, draw=none, bar shift=-0.2]
    coordinates {(2,4,90.70) (2,3,89.84) (2,2,82.72) (2,1,72.47)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=red, draw=none, bar shift=0]
    coordinates {(2,4,93.33) (2,3,90.33) (2,2,84.66) (2,1,76.69)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=brown, draw=none, bar shift=+0.2]
    coordinates {(2,4,91.67) (2,3,89.92) (2,2,82.25) (2,1,71.76)}; % Coordinates are adjusted to match the reversed ytick

\addplot3+[
    mark=none,
    blue,
    dotted,
    line width=1pt,
    nodes near coords,
    every node near coord/.append style={
        mark=none,
        fill=none,
        draw=none,
        text=black,
        font=\scriptsize,
        yshift=0pt
    }
] coordinates {
    (1.8,4,90.70) (1.8,3,89.84) (1.8,2,82.72) (1.8,1,72.47) % Coordinates are adjusted to match the reversed ytick
};

@@

\addplot3+[ybar, bar width=12pt, fill=blue, draw=none, bar shift=-0.2]
    coordinates {(3,4,83.72) (3,3,40.62) (3,2,35.66) (3,1,24.07)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=red, draw=none, bar shift=0]
    coordinates {(3,4,84.72) (3,3,40.53) (3,2,36.41) (3,1,27.40)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=brown, draw=none, bar shift=+0.2]
    coordinates {(3,4,82.58) (3,3,38.30) (3,2,33.93) (3,1,23.33)}; % Coordinates are adjusted to match the reversed ytick

\addplot3+[
    mark=none,
    blue,
    dotted,
    line width=1pt,
    nodes near coords,
    every node near coord/.append style={
        mark=none,
        fill=none,
        draw=none,
        text=black,
        font=\scriptsize,
        yshift=0pt
    }
] coordinates {
    (2.8,4,83.72) (2.8,3,40.62) (2.8,2,35.66) (2.8,1,24.07) % Coordinates are adjusted to match the reversed ytick
};
